\sys: Light-touch Data-Parallel Shell Processing

### 2020-10-05 paper/draft.tex
Teensy fix

% To have any hope of parallelizing scripts, \sys first needs to understand the parallelization characteristics of the commands they contain.
\sys aims at parallelizing data-parallel commands, \ie commands that can process their input in parallel, and encodes their characteristics by assigning them to
\emph{parallelizability classes}.
%% This information is encoded in a command's \emph{parallelizability class}.
% Intuitively, a parallelizability 
A class represents the level of synchronization required by copies of a command executing in parallel, 
  capturing only characteristics that are important for its parallel execution. % , rather than the command's full observable behavior.
\sys leans towards having a few coarse classes rather than many detailed ones---among other reasons, to simplify their understanding and use by command developers.
% Make the connections that this is like a type, that doesn't capture everything, but is good-enough

>>>>

% To have any hope of parallelizing scripts, \sys first needs to understand the parallelization characteristics of the commands they contain.
\sys aims at parallelizing data-parallel commands, \ie ones that can process their input in parallel, encoding their characteristics by assigning them to
\emph{parallelizability classes}.
%% This information is encoded in a command's \emph{parallelizability class}.
% Intuitively, a parallelizability 
A class represents the level of synchronization required by copies of a command executing in parallel, 
  capturing only characteristics that are important for its parallel execution. % , rather than the command's full observable behavior.
\sys leans towards having a few coarse classes rather than many detailed ones---among other reasons, to simplify their understanding and use by command developers.
% Make the connections that this is like a type, that doesn't capture everything, but is good-enough
